---
title: "looking at data"
runtime: shiny
output: html_document
---

This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.





## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r, echo=FALSE}
navbarPage(
  title = 'DataTable Options',
  tabPanel('Display length',     dataTableOutput('ex1')),
  tabPanel('Length menu',        dataTableOutput('ex2')),
  tabPanel('No pagination',      dataTableOutput('ex3')),
  tabPanel('No filtering',       dataTableOutput('ex4')),
  tabPanel('Individual filters', dataTableOutput('ex5')),
  tabPanel('Function callback',  dataTableOutput('ex6'))
)



renderDataTable(iris, options = list(pageLength = 10))



```

Now click on 


```{r, echo=FALSE}

library(datasets)




fluidPage(
  
  # Application title.
  titlePanel("More Widgets"),
  
  # Sidebar with controls to select a dataset and specify the
  # number of observations to view. The helpText function is
  # also used to include clarifying text. Most notably, the
  # inclusion of a submitButton defers the rendering of output
  # until the user explicitly clicks the button (rather than
  # doing it immediately when inputs change). This is useful if
  # the computations required to render output are inordinately
  # time-consuming.
  sidebarLayout(
    sidebarPanel(
      selectInput("dataset", "Choose a dataset:", 
                  choices = c("rock", "pressure", "cars")),
      
      numericInput("obs", "Number of observations to view:", 10),
      
      helpText("Note: while the data view will show only the specified",
               "number of observations, the summary will still be based",
               "on the full dataset."),
      
      submitButton("Update View")
    ),
    
    # Show a summary of the dataset and an HTML table with the
    # requested number of observations. Note the use of the h4
    # function to provide an additional header above each output
    # section.
    mainPanel(
      h4("Summary"),
      verbatimTextOutput("summary"),
      
      h4("Observations"),
      tableOutput("view")
    )
  )
)



datasetInput <- reactive({
    switch(input$dataset,
           "rock" = rock,
           "pressure" = pressure,
           "cars" = cars)
  })


output$summary <- renderPrint({
    dataset <- datasetInput()
    sapply(dataset, class)
    str(dataset)
  })



```




