---
title: "ADM2303 - Looking at data exercise"
author: Davood Astaraky
#date: "`r Sys.Date()`"
output:
  knitr:::html_vignette:
    number_sections: no
    toc: yes
    highlight: pygments
vignette: >
  %\VignetteIndexEntry{rCharts}
  %\VignetteEngine{knitr::rmarkdown}
---





```{r, warning=FALSE, message=FALSE, echo=FALSE}
library(knitr)
library(printr)
library(rCharts)
```

### Motor Trend Car Road Tests

**Description**

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).


**Format**

A data frame with 32 observations on 11 variables. Description of the variables:

```{r,eval=FALSE}
[, 1]	mpg     Miles/(US) gallon
[, 2]	cyl     Number of cylinders
[, 3]	disp    Displacement (cu.in.)
[, 4]	hp      Gross horsepower
[, 5]	drat    Rear axle ratio
[, 6]	wt      Weight (lb/1000)
[, 7]	qsec    1/4 mile time
[, 8]	vs      V/S
[, 9]	am      Transmission (0 = automatic, 1 = manual)
[,10]	gear    Number of forward gears
[,11]	carb    Number of carburetors
```


### Dataset

```{r ,results='asis',comment=NA,  tidy = F,warning=FALSE, echo=FALSE}
dt <- dTable( mtcars,
              sPaginationType= "full_numbers" )

dt$show('inline', include_assets = TRUE)
```

$\;$

$\;$


### Exercise

**Examine each of the variables and tell me what type of variable it is. **


### Source

* *Henderson and Velleman (1981), Building multiple regression models interactively. Biometrics, 37, 391–411.*

